Irt plot extra

### 2022-03-30 manuscript.Rmd
Supplementart File 1 & 2 cited

A quantitative cross-sectional fully anonymous online large-scale survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic-book "Enlighten your clock" co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux]. The landing page of the online survey had the explanatory statements where we mentioned participation was voluntary and that respondents could withdraw from participation any time without being penalized. At the beginning of the survey, for the adult participants (\>18 years) consent was recorded digitally. Under-aged participants (\<18 years) were urged to obtain assent from their parents/legal guardians. The entire survey was estimated to take \<30 minutes. Participants were not compensated. As a part of the demographic information participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language. The demographic characteristics of our sample are given in Table 1. To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention. What is 4+5?"). Participants were asked to confirm that they were participating the survey for the first time. Questions incorporating retrospective recall were all aligned to the period of "past four weeks".\
We conducted two rounds of data collections. At first, we collected data for from `r nrow(EFA.descriptives)` participants (EFA sample). In the second round we collected data from another `r nrow(CFA.descriptives)` participants (CFA sample) making a total sample of `r nrow(desctable.data)`. The data analysed in this study was collected between 17 May 2021 and 3 September 2021.

@@

Table 1 summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. (XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items. For EFA, a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]. To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per item is required to earn trustworthiness of the result. Both our EFA and CFA sample size exceeded these requirements. We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).Participants reported a diverse range of geographic location Participants indicated filling out the online survey from a diverse range of geographic locations. For a complete list of geographic locations, see **Supplementary Table 2**.

Participants in our survey aged between `r min(desctable.data$slypos_demographics_age)` to `r max(desctable.data$slypos_demographics_age)` years [EFA sample: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`; CFA sample: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 2)` years of age [Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`; CFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`]. In total `r desc_tibble[3,2]` of the participants indicated female sex [EFA: `r desc_tibble[3,3]`; CFA: `r desc_tibble[3,4]`], `r desc_tibble[4,2]` indicated male [EFA: `r desc_tibble[4,3]`; CFA: `r desc_tibble[4,4]`] and `r desc_tibble[5,2]` indicated other sex [EFA: `r desc_tibble[5,3]`, CFA: `r desc_tibble[5,4]`]. Overall, `r desc_tibble[6,2]` [EFA: `r desc_tibble[6,3]`; CFA: `r desc_tibble[6,4]`] participants indicated a gender-variant identity. In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers. For their "Occupational Status", more than half of the overall sample reported that they currently work [Overall: `r desc_tibble[9,2]`; EFA: `r desc_tibble[9,3]`; CFA: `r desc_tibble[9,4]`], whereas `r desc_tibble[10,2]` [EFA: `r desc_tibble[10,3]`; CFA: `r desc_tibble[10,4]`] reported that they go to school and `r desc_tibble[11,2]` [EFA: `r desc_tibble[11,3]`; CFA: `r desc_tibble[11,4]`] responded that they do "Neither". With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` [EFA: `r desc_tibble[13,3]`; CFA: `r desc_tibble[13,4]`] of the participants indicated that they were in a home office/ home schooling setting, while `r desc_tibble[14,2]` overall [EFA: `r desc_tibble[14,3]` ; CFA: `r desc_tibble[14,4]`] reported face-to-face work/schooling. Lastly, `r desc_tibble[15,2]` overall [EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall [EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`] filled in the "Neither (no work or school, or on vacation)" response option.

@@

```{r efagtPic1, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern observed in the large-scale survey for item 01-24. All items violated normality assumption', out.height='100%', out.width='250%'}
knitr::include_graphics('Figures/Figure2.png')

@@

```{r efagtPic2, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern observed in the large-scale survey for item 25-48. All items violated normality assumption', out.height='100%', out.width='250%'}
knitr::include_graphics('Figures/Figure3.png')

@@

**Supplementary Figure 1** summarizes the univariate descriptive statistics for the 48 items in the EFA sample (n =`r nrow(EFA.data)`. Here also our data violated univariate normality [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970]. Multivariate skew was `r printnum(mardia$b1p)` (p \<0.001) and multivariate kurtosis was `r printnum(mardia$b2p)` (p \<0.001). The corrected item-total correlation ranges between `r apa(low.r.corec,2,F)` -`r apa(high.r.corec,2,F)`. However, no item was discarded based on descriptive statistics or item analysis.

@@

Scree plot ( Figure \@ref(fig:efa-plot-print)-B) suggested a six-factor solution. However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print)C) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items (cross-loading items and poor factor loading (\<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30. Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:efa-plot-print)D) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (**Supplementary Table 4**).

@@

Table \@ref(tab:tabCfa) summarizes the CFA fit indices of our fitted model. Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [`r Hmisc::label(sem.data$item32)`; `r Hmisc::label(sem.data$item33)`] and 16-17 [`r Hmisc::label(sem.data$item16)`; `r Hmisc::label(sem.data$item17)`]. Items pair 32-33 stemmed from the preference of dimming electric device's brightness before bed time and items pair 16 and 19 stemmed from the preference of using blue filtering or coloured glasses during the daytime. Nevertheless, SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`). Further by allowing one pair of items (30-41) [`r Hmisc::label(sem.data$item30)`; `r Hmisc::label(sem.data$item41)`] to covary their error variance and discarding two item (item 37 & 26) for possible cross-loading, our model attained the best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]). Internal consistency ordinal $\alpha$ for the five factors of LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)` respectively. Internal consistency McDonald's $\omega_t$ coefficient for the total scale was `r apa(rel.k[5,6],2,F)`. Figure \@ref(fig:figcfa) depicts the obtained CFA structure. **Supplementary Figure 2** depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.

@@

## Secondary Analysis: Grade Level Identification and Semantic Scale Network Analysis
Flesch-Kincaid grade level [@flesch1948new] analysis on the 23 items indicated required educational grade level was 3.33 and with a age above 8.33. This indicated our scale will be understandable to students of grade four and aged at least 8.33. 
Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that LEBA (23 items) appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite]. The cosine similarities lie between .47 to .51.

@@

We fitted each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690). Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**). Examination of the item information curve (**Supplementary Figure 3**) indicated five items (1, 25, 38, 30, & 41) had relatively flat information curves (I($\theta$) \<.20). We discarded those items which yielded a short form of LEBA with 5 factors and 18 items.

>>>>

A quantitative cross-sectional fully anonymous online large-scale survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic-book "Enlighten your clock" co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux]. The landing page of the online survey had the explanatory statements where we mentioned participation was voluntary and that respondents could withdraw from participation any time without being penalized. At the beginning of the survey, for the adult participants (\>18 years) consent was recorded digitally. Under-aged participants (\<18 years) were urged to obtain assent from their parents/legal guardians. The entire survey was estimated to take \<30 minutes. Participants were not compensated. As a part of the demographic information participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language. The demographic characteristics of our sample are given in Table 1. To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention. What is 4+5?"). Participants were asked to confirm that they were participating the survey for the first time. Questions incorporating retrospective recall were all aligned to the period of "past four weeks".\
We conducted two rounds of data collection. At first, we collected data for from `r nrow(EFA.descriptives)` participants (EFA sample). In the second round we collected data from another `r nrow(CFA.descriptives)` participants (CFA sample) making a total sample of `r nrow(desctable.data)`. The data analysed in this study was collected between 17 May 2021 and 3 September 2021.

@@

Table 1 summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. (XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items. For EFA, a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]. To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per item is required to earn trustworthiness of the result. Both our EFA and CFA sample size exceeded these requirements. We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones). Participants reported a diverse range of geographic location Participants indicated filling out the online survey from a diverse range of geographic locations. For a complete list of geographic locations, see **Supplementary Table 2**.

Participants in our survey aged between `r min(desctable.data$slypos_demographics_age)` to `r max(desctable.data$slypos_demographics_age)` years [EFA sample: `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])` to `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`; CFA sample: `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`to `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 2)` years of age [Overall: `r mean(desctable.data$slypos_demographics_age)`± `r sd(desctable.data$slypos_demographics_age)`; EFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`± `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`; CFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`± `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`]. In total `r desc_tibble[3,2]` of the participants indicated female sex [EFA: `r desc_tibble[3,3]`; CFA: `r desc_tibble[3,4]`], `r desc_tibble[4,2]` indicated male [EFA: `r desc_tibble[4,3]`; CFA: `r desc_tibble[4,4]`] and `r desc_tibble[5,2]` indicated other sex [EFA: `r desc_tibble[5,3]`, CFA: `r desc_tibble[5,4]`]. Overall, `r desc_tibble[6,2]` [EFA: `r desc_tibble[6,3]`; CFA: `r desc_tibble[6,4]`] participants indicated a gender-variant identity. In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers. For their "Occupational Status", more than half of the overall sample reported that they currently work [Overall: `r desc_tibble[9,2]`; EFA: `r desc_tibble[9,3]`; CFA: `r desc_tibble[9,4]`], whereas `r desc_tibble[10,2]` [EFA: `r desc_tibble[10,3]`; CFA: `r desc_tibble[10,4]`] reported that they go to school and `r desc_tibble[11,2]` [EFA: `r desc_tibble[11,3]`; CFA: `r desc_tibble[11,4]`] responded that they do "Neither". With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` [EFA: `r desc_tibble[13,3]`; CFA: `r desc_tibble[13,4]`] of the participants indicated that they were in a home office/ home schooling setting, while `r desc_tibble[14,2]` overall [EFA: `r desc_tibble[14,3]` ; CFA: `r desc_tibble[14,4]`] reported face-to-face work/schooling. Lastly, `r desc_tibble[15,2]` overall [EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall [EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`] filled in the "Neither (no work or school, or on vacation)" response option.

@@

```{r efagtPic1, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern observed in the large-scale survey for item 01-24. All items violated normality assumption.', out.height='100%', out.width='250%'}
knitr::include_graphics('Figures/Figure2.png')

@@

```{r efagtPic2, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern observed in the large-scale survey for item 25-48. All items violated normality assumption.', out.height='100%', out.width='250%'}
knitr::include_graphics('Figures/Figure3.png')

@@

**Supplementary Figure 1** summarizes the univariate descriptive statistics for the 48 items in the EFA sample (n =`r nrow(EFA.data)`). Here also our data violated univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970]. Multivariate skew was `r printnum(mardia$b1p)` (p \<0.001) and multivariate kurtosis was `r printnum(mardia$b2p)` (p \<0.001). The corrected item-total correlation ranges between `r apa(low.r.corec,2,F)` -`r apa(high.r.corec,2,F)`. However, no item was discarded based on descriptive statistics or item analysis.

@@

Scree plot ( Figure \@ref(fig:efa-plot-print)-B) suggested a six-factor solution. However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print)-C) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items (cross-loading items and poor factor loading (\<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30. Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:efa-plot-print)-D) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (**Supplementary Table 4**).

@@

Table \@ref(tab:tabCfa) summarizes the CFA fit indices of our fitted model. Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)`[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [`r Hmisc::label(sem.data$item32)`; `r Hmisc::label(sem.data$item33)`] and 16-17 [`r Hmisc::label(sem.data$item16)`; `r Hmisc::label(sem.data$item17)`]. Items pair 32-33 stemmed from the preference of dimming electric device's brightness before bed time and items pair 16 and 19 stemmed from the preference of using blue filtering or coloured glasses during the daytime. Nevertheless, SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`). Further by allowing one pair of items (30-41) [`r Hmisc::label(sem.data$item30)`; `r Hmisc::label(sem.data$item41)`] to covary their error variance and discarding two item (item 37 & 26) for possible cross-loading, our model attained the best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]). Internal consistency ordinal $\alpha$ for the five factors of LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)` respectively. As such, we accept this model thus finalizing the long Form of LEBA with 23 items. The items are provided in the **Supplementary File 1**.  Internal consistency McDonald's $\omega_t$ coefficient for the total scale was `r apa(rel.k[5,6],2,F)`. Figure \@ref(fig:figcfa) depicts the obtained CFA structure. **Supplementary Figure 2** depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.

@@

## Secondary Analysis: Grade Level Identification and Semantic Scale Network Analysis
Flesch-Kincaid grade level [@flesch1948new] analysis on the 23 items indicated required educational grade level was 3.33 and with a age above 8.33 years. This indicated our scale will be understandable to students of grade four and aged at least 8.33. 
Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that LEBA (23 items) appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite]. The cosine similarities lie between .47 to .51.

@@

We fitted each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690). Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**). Examination of the item information curve (**Supplementary Figure 3**) indicated five items (1, 25, 38, 30, & 41) had relatively flat information curves (I($\theta$) \<.20). We discarded those items which yielded a short form of LEBA with 5 factors and 18 items (**Supplementary File 2**).
